Presentation Plan\\ FF-Replan: \& RFF\@: Exploiting classical AI planning for uncertain and probabilistic domains

### 2014-03-05 presentation-plan/Plan_presentation_monday.tex
Typos

Growing plants is an extremely uncertain domain. When everything goes well, it should be fine to water it once a week. However my room environment has proven to be an uncertain domain where wind, temperature and sunlight severely impacts my abality to plan for nurturing my plants.

@@

\subsubsection{Problem definition}
Probabilistic planning is naturally formulated using Markov Decision Processes. These probabilistic planners focus on the entire state space. Deterministic planning has developed heuristic funtions enabling exploration of restricted portions of the state space enroute to the goal state. This enables the planner to account for unexpected states rather than ending up in a dead-end. MDP's had been the standard in planning algorithms [FOR HOW LONG]? However by relying on search and current available processing power, deterministic planners function with enormous speed and efficiency. This has been a motivation for combining deterministic and probabilistic planners in the planning communities.

@@

\subsubsection{Points of improvement}
\begin{enumerate}
	\item
	\item
	\item Adaptively repair the partial policy
	\item Sampling of the grounded goals and testing with a relaxed reachability analysis
	\item This is solved by using the all-outcomes approach
	\item It does not look ahead, but only adjusts when something unexpected has occured

@@

\subsubsection{Things to look into}
\begin{itemize}
	\item How is the exploding block domain currently tackled as during 2004 and 2006 no one really was able to solve it?
	\item Is the planning time still a problem as much as it proved to be then with the bigger domains?
	\item Using hindsight optimization might be more realistic as it is less optimistic. It will eventuall increase the process time, but increase the robustness of the system.
	\item Using a look ahead policy enables the planner to avoid dead ends, it however does not avoid cycles.
\end{itemize}

@@

\emph{state that RFF is not an optimization algorithm, but only asks whether there exists a policy whose probability of reaching a goal-state in non zero and whose probability of replanning when executed is less than p}

@@

\emph{We should also show their lemma's including the critism on their proof, as it is not sound}

@@

\subsubsection{Criticism on the paper}
\begin{itemize}
	\item They redefine the planning problem by adding a probability threshold. They use this to their advantage by stating their algorithm is complete as it finds all solutions in this planning problem. When not defining this threshold, it obviously doesn't always find all possible solutions as it neglects the lest probable solutions.  
	\item In the experiment section they clearly state that the search-and-rescue domain cause problems for the algorithm, however they choose not to even display the results as the RFF algorithm is not designed for planning problems without goal states. This displayes that RFF is in fact not a very good general planning algorithm. 
\end{itemize}

@@

\subsubsection{Interesting directions to look into}
generalizing the planning framework to hybrid MDPs in which there are both discrete and continuous valued state variables. The factored MDP representations in RFF will be the basis of these generalizations. There were currently investigation which classical planners were suitable to incoorporate in RFF.

>>>>

Growing plants is an extremely uncertain domain. When everything goes well, it should be fine to water it once a week. However my room environment has proven to be an uncertain domain where wind, temperature and sunlight severely impacts my ability to plan for nurturing my plants.

@@

\subsubsection{Problem definition}
Probabilistic planning is naturally formulated using Markov Decision Processes. These probabilistic planners focus on the entire state space. Deterministic planning has developed heuristic functions enabling exploration of restricted portions of the state space enroute to the goal state. This enables the planner to account for unexpected states rather than ending up in a dead-end. MDP's had been the standard in planning algorithms [FOR HOW LONG]? However by relying on search and current available processing power, deterministic planners function with enormous speed and efficiency. This has been a motivation for combining deterministic and probabilistic planners in the planning communities.

@@

\subsubsection{Points of improvement}
\begin{enumerate}
	\item
	\item
	\item Adaptively repair the partial policy
	\item Sampling of the grounded goals and testing with a relaxed reachability analysis
	\item This is solved by using the all-outcomes approach
	\item It does not look ahead, but only adjusts when something unexpected has occurred

@@

\subsubsection{Things to look into}
\begin{itemize}
	\item How is the exploding block domain currently tackled as during 2004 and 2006 no one really was able to solve it?
	\item Is the planning time still a problem as much as it proved to be then with the bigger domains?
	\item Using hindsight optimization might be more realistic as it is less optimistic. It will eventually increase the process time, but increase the robustness of the system.
	\item Using a look ahead policy enables the planner to avoid dead ends, it however does not avoid cycles.
\end{itemize}

@@

\emph{state that RFF is not an optimization algorithm, but only asks whether there exists a policy whose probability of reaching a goal-state in non zero and whose probability of replanning when executed is less than $\rho$}

@@

\emph{We should also show their lemma's including the criticism on their proof, as it is not sound}

@@

\subsubsection{Criticism on the paper}
\begin{itemize}
	\item They redefine the planning problem by adding a probability threshold. They use this to their advantage by stating their algorithm is complete as it finds all solutions in this planning problem. When not defining this threshold, it obviously doesn't always find all possible solutions as it neglects the lest probable solutions.
	\item In the experiment section they clearly state that the search-and-rescue domain cause problems for the algorithm, however they choose not to even display the results as the RFF algorithm is not designed for planning problems without goal states. This displays that RFF is in fact not a very good general planning algorithm.
\end{itemize}

@@

\subsubsection{Interesting directions to look into}

Generalizing the planning framework to hybrid MDPs in which there are both discrete and continuous valued state variables. The factored MDP representations in RFF will be the basis of these generalizations. There were currently investigation which classical planners were suitable to incorporate in RFF.
